### 2024-08-21 paper.tex
start on alternative-characterization proof
continue
some notation

\subsection{Springer fibers in \(\gl_m\)}
Now we let \(\mathcal{N}\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}\) the variety of Borel subalgebras of \(\gl_m\).
Let \(H \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
The variety of Borel subalgebras of \(\gl_m\) is \(\mathcal{B} = \{gHg^{-1} : g \in \GL_m\}\).
Thus, the Springer fiber at \(X \in \mathcal{N}\) is 
\[S_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
\begin{definition}
    A \emph{flag} \((V_i)\) of \(\mathbb{C}^m\) is a sequence of subspaces
    \[0 = V_0 \subseteq V_1 \subseteq \cdots \subseteq V_m = \mathbb{C}^m,\]
    where \(\dim V_i = i\).
\end{definition}
We say that \(X \in \gl_m\) \emph{preserves} a flag \((V_i)\) if \(\forall i. \; XV_i \subseteq V_i\).
Note that \(X \in \mathcal{N}\) preserves a flag \((V_i)\) if and only if \(\forall i. \; XV_i \subseteq V_{i - 1}\).
\par The simplest flag is the \emph{standard flag} \((E_i)\), where \(E_i := \langle e_1, ..., e_i \rangle\).
Note that the group \(H\) is exactly the subset of \(\gl_m\) which preserves \(E_i\).
\par We can think of \(\mathcal{B}\) as the set of flags of \(\mathbb{C}^m\), via the correspondence 
\[gHg^{-1} \leftrightarrow (gE_i).\]
Note that \(X\) preserves \((gE_i)\) if and only if \(X \in gHg^{-1}\).
Thus, we may write the Springer fiber at \(X \in \mathcal{N}\) in terms of flags, as 
\[S_X = \{(gE_i) : X \in gHg^{-1}\} = \{(V_i) : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]

@@

\subsection{A study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k := \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).

>>>>

\subsection{Springer fibers in \(\gl_m\)}
Now we let \(\mathcal{N}_m\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
Let \(H \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
The variety of Borel subalgebras of \(\gl_m\) is \(\mathcal{B} = \{gHg^{-1} : g \in \GL_m\}\).
Thus, the Springer fiber at \(X \in \mathcal{N}\) is 
\[S_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
\begin{definition}
    A \emph{flag} \((V_i)\) of \(\mathbb{C}^m\) is a sequence of subspaces
    \[0 = V_0 \subseteq V_1 \subseteq \cdots \subseteq V_m = \mathbb{C}^m,\]
    where \(\dim V_i = i\).
\end{definition}
We say that \(X \in \gl_m\) \emph{preserves} a flag \((V_i)\) if \(\forall i. \; XV_i \subseteq V_i\).
Note that \(X \in \mathcal{N}\) preserves a flag \((V_i)\) if and only if \(\forall i. \; XV_i \subseteq V_{i - 1}\).
\par The simplest flag is the \emph{standard flag} \((E_i)\), where \(E_i := \langle e_1, ..., e_i \rangle\).
Note that the group \(H\) is exactly the subset of \(\gl_m\) which preserves \(E_i\).
\par We can think of \(\mathcal{B}\) as the set of flags of \(\mathbb{C}^m\), via the correspondence 
\[gHg^{-1} \leftrightarrow (gE_i).\]
Note that \(X\) preserves \((gE_i)\) if and only if \(X \in gHg^{-1}\).
Thus, we may write the Springer fiber at \(X \in \mathcal{N}\) in terms of flags, as 
\[S_X = \{(gE_i) : X \in gHg^{-1}\} = \{(V_i) : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]

@@

\subsection{A study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
% Now, we also set \(q_{i_{-1}} := 0\), and \(p_{i_0} := \infty\) (just a symbol which is bigger than any integer).

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We have two cases: either \(S\) is empty, or not.
    \par If \(S\) is empty

    and let \(k = \min S\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
    That is, need to show that \(\)
    \par Let \(l \in \{0, ..., r\}\), and suppose \(q_i < q_{i_l}\).
    Then, since \(\max_{j : q_j < q_{i_l}} p_j = p_{i_{l + 1}}\), we have \(p_i \leq p_{i_{l + 1}}\).
    This implies that 
\end{proof}
